Research Notes

### 2018-02-27 writups/notes.tex
stash

Since we're much more interested in the $z$ behavior, we will set the $z$ axis
to be further away. Let's choose $\rho_0 = 1, L_x = 10, L_z = 20, k_x = 2, k_z =
1, H = 5, g = 10$ which constrains $N^2 \equiv g/H = 1, \omega^2 = \frac{4}{5 +
1/100}$. Some considerations:
\begin{itemize}
    \item $\frac{1}{k_xH}, \frac{1}{k_zH}$ are $1/10, 1/5$ respectively,
        small-ish but $L_Z = 8H$ so we should be able to see the $e^{z/2H}$
        behavior well.

    \item The vertical phase velocity is $\frac{\omega}{k_z} \sim 1$, so we
        should simulate at least out to $t = 20$ for the wave to fully propagate
        to the boundary.
\end{itemize}

\subsection{Sommerfield/Radiative BCs}

\section{(Algebra) The Anelastic/Boussinesq Approximations}

@@

\chapter{2D Wave Breaking in Atmospheres}

\section{Dynamical Setup}

TODO (fluid equations, driven on bottom, parameters)

\section{Boundary Conditions}

TODO (periodic in x, show that right number of BCs in $z$, discuss whether gauge
choice).

\section{Simulation}

TODO (CFL conditions etc.)

>>>>

From here we can just tweak the parameters until we get something useful, can
look at the videos. Note that we should simulate until at least $T >
\frac{2L_z}{v_{p, z}}$ the $z$ phase space velocity, so we can capture any
reflections off the boundary. Turns out both Dirichlet and Neumann BCs give
strong reflections that produce standing waves in the $z$ and traveling waves in
the $x$.

\subsection{Supressing Reflection}

Sourced from \url{https://people.maths.ox.ac.uk/trefethen/6all.pdf}. There are
largely two ways to do this. The first is to add a damping zone, a region in
which $\dot{q} = -q/\tau_d(z)$ where $\tau_d(0) = 0$ and increases to some
non-small number for some $z_0$ beyond which we want damping.

This requires we compute a ton of extra points though. Ideally, we want to use
BCs. Based on our explicit solution \autoref{eq:strat.full_sol} we might expect
to write something like $\pd{u_{1z}}{z} = \frac{1/2H +
ik_z}{\mp i\omega}\pd{u_{1z}}{z} \approx \pm \frac{k_z}{\omega}\pd{u_{1z}}{z}$.
For an outgoing wave we expect to choose the negative sign.

\section{(Algebra/Optional) The Anelastic/Boussinesq Approximations}

@@
